---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

<!-- badges: start -->
[![lifecycle](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://www.tidyverse.org/lifecycle/#experimental)
[![CRAN status](https://www.r-pkg.org/badges/version/htmlvault)](https://CRAN.R-project.org/package=htmlvault)
[![R build status](https://github.com/dirkschumacher/htmlvault/workflows/R-CMD-check/badge.svg)](https://github.com/dirkschumacher/htmlvault/actions)
<!-- badges: end -->

# Embed files in self-decrypting html pages

This package can encrypt arbitrary files such as PDF reports or RMarkdown exports and embed them in an html document that can decrypt itself using [libsodium](https://download.libsodium.org/doc/). The resulting html file is fully portable and just requires a browser to be used.

*Use at your own risk. Feedback and bug reports very welcome!*

## Installation

``` r
# install.packages("htmlvault") not yet
```

``` r
remotes::install_github("dirkschumacher/htmlvault")
```

## Functions

The package currently has just one function `htmlvault_encrypt_file` to encrypt files and create a new self-decrypting html file.

### Encrypt files

First we load the package and create a random secret with which we encrypt the document:
```{r}
library(htmlvault)
key <- sodium::random(32)
message(sodium::bin2hex(key))
```

Then we call `htmlvault_encrypt_file` with the computed key.

```{r}
htmlvault_encrypt_file(
  path = "devel/example/test.html",
  output_path = "docs/test.encrypted.html",
  key = key
)
```
It uses the `mime` package to figure out the MIME type of the input file and thus supports many different file types. Below are two examples encrypting PDF and Word documents.

```{r}
htmlvault_encrypt_file(
  path = "devel/example/test.pdf",
  output_path = "docs/test.encrypted_pdf.html",
  key = key
)
```

```{r}
htmlvault_encrypt_file(
  path = "devel/example/test.docx",
  output_path = "docs/test.encrypted_word.html",
  key = key
)
```

You can take a look at the exported files [here](https://dirkschumacher.github.io/htmlvault/test.encrypted.html), [here](https://dirkschumacher.github.io/htmlvault/test.encrypted_pdf.html) and [here](https://dirkschumacher.github.io/htmlvault/test.encrypted_word.html) and use the key printed above to decrypt it.

## Inspiration

Inspired and based on the work by @derhuerst on [self encrypting html pages](https://github.com/derhuerst/self-decrypting-html-page).

## License

MIT

## Security

* The package uses `libsodium` for encryption and includes the code to decrypt as javascript in the resulting html file.
* The security depends on your key strength, the correctness of this package, the `sodium` R package and the `libsodium` library.
* Beware: the current implementation does not encrypt the MIME type of your document. For example, anybody sees that the encrypted document is of type PDF, but the actual content is just accessible after decryption.

## Development

In `devel/r-encrypted-html-template` the code to generate the javascript file is contained. In order to update the template, you have to run the following:

* In `devel/r-encrypted-html-template` run `npm run build`. This creates a new version of the template and copies it to `devel/html-template.js`. It also creates a file called `JSLICENSES.txt` that contains all licenses of used node packages.
* In `devel` run `combine.R`. This generates the file report template and copies it to `inst/html-template.html`. This template is then used within the R package to generate encrypted html files.
